---
title: "Association_rules_ok_cupis"
author: "Sowmya Chenthi Kumar"
date: "2/26/2021"
output: pdf_document
---

Read the required data set'
```{r}
data_okcupid <- read.csv("D:/UBCO_lecture_materials/BLOCK4/DATA572-SUPERVISED LEARNING/okcupidprofiles.csv")
head(data_okcupid)
```

Have a look at the data as a possible summary analysis:
```{r}
summary(data_okcupid)
```


Look for the possible numeric columns in the dataset:
```{r}
data_okcupid$age <- as.numeric(data_okcupid$age)
data_okcupid$height <- as.numeric(data_okcupid$height)

```

There are few missing values present in the dataset and as the dataset is large we can safely eliminate them 

Lets carry out the required wrangling with our dataset:

```{r}
# First lets remove all the rows that have the NA values present:
data_okcupid <- data_okcupid[complete.cases(data_okcupid),]
data_okcupid[27939:27944,1]
```
There are some values in the smoke column which has the data as "" and we can replace them with the na values:

```{r}
data_okcupid$smokes[data_okcupid$smokes == ""] <- NA
names(table(data_okcupid$smokes)) 

```

Finally a summary of the wrangled dataset:
```{r}
summary(data_okcupid)
```

Discrete the numeric columns into factors by creating bins:

First lets carry out the process with age
```{r}
data_okcupid$age <- discretize(data_okcupid$age, method = "interval", breaks = 4)
unique(data_okcupid$age)
```

Next with height:
```{r}
data_okcupid$height <- discretize(data_okcupid$height, method = "interval", breaks = 4)
unique(data_okcupid$height)
```

Now we run the Apriori in the default specification:
```{r}
algo_cupid <- apriori(data_okcupid)
```
```{r}
summary(algo_cupid)
```

Setting the reuired threshold and then running the algorithm again:

```{r}
algo_cupid_thres <- apriori(data_okcupid, parameter = list(supp= 0.6, conf= 0.8))
```

```{r}
summary(algo_cupid_thres)
```

Lets inspect further to understand first by support:

```{r}
inspect(sort(algo_cupid_thres, by= "support")[1:10])
```

```{r}
inspect(sort(algo_cupid_thres, by= "lift")[1:10])
```
```{r}
inspect(sort(algo_cupid_thres, by= "confidence")[1:10])
```

